# Efficient learning

**Learning objectives:**

-   Use R's built-in (and packaged) help system to learn.
-   Read about R use cases and developments.
-   Get help online.
-   Learn from books and tutorials.
-   Teach to learn.

## R help {-}

Multiple levels of help in R:

-   `??topic` == `help.search("topic")`
-   `apropos()` (print object matching string, no slide for this one)
-   `browseVignettes()`
-   `?function` == `help("function")`
-   Read source code
-   `{swirl}` & `{learnr}`

## help dot search {-}

You can super-charge `??`!

```{r 10-help.search, eval = FALSE}
help.search(pattern, fields = c("alias", "concept", "title"),
            apropos, keyword, whatis, 
            ignore.case = TRUE,
            package = NULL, lib.loc = NULL,
            help.db = getOption("help.db"),
            verbose = getOption("verbose"),
            rebuild = FALSE, agrep = NULL, use_UTF8 = FALSE,
            types = getOption("help.search.types"))
```

-   `apropos` Search topics & title (separate from `pattern`)
-   `keyword` Specifically search `keywords` field
-   `whatis` Search in topics
-   `agrep` Specify how fuzzy to be (see `agrep()` function)
-   `types` "vignette", "help", and/or "demo"

## browseVignettes {-}

Source code for `browseVignettes()` led me to `tools::getVignetteInfo()`

```{r 10-getVignetteInfo, eval = FALSE}
tibble::as_tibble(tools::getVignetteInfo()) |> 
  dplyr::glimpse()

#> Rows: 519
#> Columns: 7
#> $ Package <chr> "attempt", "attempt", "attempt", "attempt", "atte…
#> $ Dir     <chr> "mypath/attempt", "mypath/attempt", "mypath/attem…
#> $ Topic   <chr> "c_adverbs", "e_conditions", "d_if", "a_intro_att…
#> $ File    <chr> "c_adverbs.Rmd", "e_conditions.Rmd", "d_if.Rmd", …
#> $ Title   <chr> "Adverbs", "Condition handling", "If", "Intro to …
#> $ R       <chr> "c_adverbs.R", "e_conditions.R", "d_if.R", "a_int…
#> $ PDF     <chr> "c_adverbs.html", "e_conditions.html", "d_if.html…
```

## help {-}

```{r 10-help, eval = FALSE}
help(topic, package = NULL, lib.loc = NULL,
     verbose = getOption("verbose"),
     try.all.packages = getOption("help.try.all.packages"),
     help_type = getOption("help_type"))
```

-   `help_type` "text", "html", or "pdf"

## R source code {-}

-   Learn to use F2 in RStudio!
-   `pkgname:::` to dig through internals
-   `usethis::create_from_github()`
-   [cran org on github](https://github.com/cran)
    -   Eg [`expr()` on CRAN](https://github.com/search?q=org%3Acran+%2F%28%5E%7C%5Cs%2B%7C%3A%3A%29expr%5C%28%2F&type=code)

## swirl & learnr {-}

-   {swirl} hasn't been updated in 3 years
-   {learnr} is Posit's teaching package
    -   Some in Tutorial tab in RStudio
    -   [Examples](https://rstudio.github.io/learnr/articles/examples.html)
    -   `learnr::available_tutorials()`
    -   `learnr::run_tutorial("pca_recipes", package = "learntidymodels")`
    -   I really need to experiment with this one!

## R journals, etc {-}

-   Package websites have become super helpful
-   Posit has [Quarto versions of core R manuals](https://rstudio.github.io/r-manuals/)
-   We've talked about doing an "R Journal Club" at R4DS, watch for that!
-   [rdrr.io](https://rdrr.io/) & [R Universe](https://r-universe.dev/search/)
-   [R-bloggers](https://www.r-bloggers.com/)
-   [rOpenSci Blog](https://ropensci.org/blog/)
-   Others?

## Reprexes & online help {-}

-   Use [{reprex}](https://cran.r-project.org/package=reprex) for **repr**oducible **ex**amples
-   [R4DS #help-\* channels](https://r4ds.io/join)
-   [Posit Community](https://community.rstudio.com/)
-   [discoRd](https://discord.gg/UBuG5hzu)
-   #RStats on Mastodon, LinkedIn, & Twitter
-   [R tag on StackOverflow](https://stackoverflow.com/questions/tagged/r)
    -   [R wiki on StackOverflow](https://stackoverflow.com/tags/r/info)

## Book clubs! {-}

-   Current (2023-06-02):
    -   20 "books"
    -   24 cohorts
-   Past:
    -   85 YouTube playlists
    -   1337 videos
-   See #book_club-announce & #book_club-\* on [R4DS Slack](https://r4ds.io/join)

## Teach {-}

> "By teaching, we learn."

-   Answer questions on R4DS!
    -   [r4ds.io/mentordash](https://r4ds.io/mentordash) 👈 unanswered questions
-   Lead a discussion in a book club!
-   Write a blog!
-   Improve package documentation! 
-   Write a package!
-   Write a book!

## Meeting Videos {-}

### Cohort 1 {-}

`r knitr::include_url("https://www.youtube.com/embed/URL")`

<details>
<summary> Meeting chat log </summary>

```
LOG
```
</details>
